\TheTitle

### 2015-08-15 linvis.tex
Design: CLI-Shell, Web-based tool
Re-writing design section, talking about the components of the design. Also
including information on the original design of the command line navigation
interface. A new picture is probably a good idea for the shell.

% \section{Design}
% 
% The goal is to build a system that allows users to easily navigate and
% understand the changes within the kernel. We provide a mechanism for performing
% searches to filter out irrelevant commits and merges, and only work with
% information that they are interested in. At the top level, the commits are
% grouped by release version. \evan{We currently do not provide a mechanism for
% checking real versions and release candidates\ldots Might be useful to at least
% note in search results section}.
% 
% 
% information as
% possible to narrow the results that we wanted to return. Right now, the largest
% set of data that a search could return is the entire set of commits that
% pertain to a given release. While this set is massive, it pales in comparison
% to every commit and merge generated for all versions of the kernel. From there,
% the design is centered around the merge tree. These are all of the commits and
% merges that eventually are merged by a top-level merge into the kernel. The
% design centers around a vine-shape. The top-level merges form a linked list,
% each node being a logical section within the kernel. These sections are defined
% by Linus. Within each of these top-level merges is a tree of merges and
% commits. The merges form the inner-nodes, and the commits form the leaf-nodes.
% 
% \evantodo{Make a vine diagram}
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{}
% % \end{figure}
% 
% 
% Different kinds of users need to be able to use the tool differently.
% Some users may be looking for a top-down approach, trying to find the merge
% closest to the top-level merge that works with a given set of files. Other uses
% may be looking for a bottom-up approach, given a commit, what top-level merge
% includes this commit. Other users are interested in what happens in a given
% release cycle without any other requirements.
% 
% \subsection{Architecture}
% 
% % Database
% We split the data presented among five tables; commits, filesmod, logs,
% pathtomerge, and releases. The commits table stores the metadata about a given
% commit or merge. This includes the author, the authored date, the committer,
% commit date, and the file-level diff. The filesmod table stores the information
% about the files modified in a commit. We have the commit id, or cid, of the
% commit, the filename, the number of lines added and the number of lines removed
% from the file. There may be multiple files within a given commit, and there may
% be multiple commits editing the same file, the database uses an index as the
% primary key, though the primary key could be the cid, filename pair.
% 
% % Tables
% % commits
% % filesmod
% % logs
% % pathtomerge
% % releases
% 
% %
% 
% 
% \subsection{Navigation}
% 
% A user is greeted by the search screen. We break the kernel down by release,
% limiting the maximum information a user can query to help minimize being
% overwhelmed. From there, users can either search by author name, commit id, or
% keyword from the log preview. A user may also request the top-level merges that
% meet the requirements. If the checkbox is unchecked, a user is able to query
% all commits and merges that happened in the selected release cycle. If the box
% is checked, the user will get all of the top-level merges in the release cycle
% that contain a commit or merge that match the given criteria. If no criteria
% are provided and the box is checked, the user will simply be given all
% top-level merges for that release cycle. This helps separate the use-cases,
% allowing users wanting the bottom-up approach to perform searches, and users
% wanting a top-down approach to perform searches.
% 
% Once a user has found either the top-level merge or commit that they are
% interested in, they should be able to move freely between the commits and
% merges in the tree. We use three mechanisms to provide better navigation
% through the tree. The tree view, the list tree, and breadcrumbs.
% 
% The tree view provides most of the
% navigational functionality, allowing users to jump to any commit or merge in
% the current tree. The main tree view displays all the commits and merges, the
% root is the top-level merge of all the commits and merges in the group. Users
% are able to see all commits and merges of all the merges.
% 
% \evantodo{Picture of tree}
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{}
% % \end{figure}
% 
% The list tree shows the merges and commits of the current subtree, built as
% nested lists of links to the respective commits and merges. The information in
% this tree is a subset of the main tree view, providing a method users with a
% view of what commits and merges are below the current commit or merge. If the
% current position is a commit, the tree will be empty, as commits are leaf
% nodes in the tree representation. This is designed for letting users move
% quickly down in the tree.
% 
% \evantodo{Picture of list tree}
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{}
% % \end{figure}
% 
% 
% The breadcrumbs show the path of merges that are above the current commit or
% merge, up to the top-level merge. This allows users a fast way to move up in
% the tree.
% 
% \evantodo{Picture of breadcrumbs}
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{}
% % \end{figure}
% 
% 
% \subsection{Information and Presentation}
% 
% Navigation is only effective if the destination contains the desired
% information. We present the commit log, what files were edited, and what
% modules were edited at a given commit or merge. Normal tools are unable to
% provide information about what files are edited in a merge because they do no
% use the tree structure. From our tree structure, we are able to traverse the
% subtree, making note of what files are edited and how many lines of code are
% added and removed at every commit.
% 
% \evantodo{Picture of files}
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{}
% % \end{figure}
% 
% The tree views provide navigation, but are also able to present implied
% information about the depth and number of commits in a given merge.
% 
% \section{Discussion}
% 
% Our search provides mechanisms for users looking for top-down and bottom-up
% approaches. In figures \ref{fig:AndrewMortonMerges} and \ref{fig:AndrewMorton}
% we see the difference in responses when looking for the merges by Linus and the
% commits authored by Andrew Morton.
% \evantodo{Picture of results for top-down and bottom-up}
% 
% %% http://localhost:8080/search?version=Linux+3.14&commit_date_begin=&commit_date_end=&search-text=Morton&search-type=Author&merges=on
% 
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{fig:AndrewMortonMerges}
% % \end{figure}
% %
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{fig:AndrewMorton}
% % \end{figure}

>>>>

\section{Design}

The goal is to build a tool that make navigation of the kernel commit
information simpler, while providing an explanation of the changes occurring at
each commit and merge. Part of making the information usable is to narrow the
results down into only the information that is relevant to what the user is
looking for.

\subsection{Command-line Shell}

Our initial intuition was to work with the commits and merges as trees, like in
a file structure. There are many similarities in the structure of a file system
and the structure of the commit information within the kernel. The primary
similarity is that they are both trees, and both trees are generally fairly
shallow and very wide. File systems have been around for quite some time, and
there are many tools for visualizing and working withe the file structure. The
first tool was the command-line. We built a small command-line shell
(\ref{fig:shell}) that allowed navigation through the commit and merges instead
of files and directory. The shell design permitted a user to move through the
merges like they would through directories. They could use the cat command to
see the preview of the log, or the more command to see the preview and what
files were edited in the commit and how many lines were added and removed from
each file.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/shell.png}
	\caption{Shell Design}
	\label{fig:shell}
\end{figure}

\evantodo{Put this in discussion section}
The main issue with this design is that a user will always move from the
top-down without any additional filtering. Furthermore, it presents the user
with the commit hashes, which provide no explanation of what the commit or
merge may contain.

\subsection{Web-based Tool}

There are multiple reasons for building the system into a web-based tool.
Putting the tool onto the web enables users to use the system without having to
install anything, making the system platform independent. A web-based tool can
utilize more interactive means of navigation, and provide a better explanation
of what each commit or merge may contain.

The web-based tool provides many mechanisms to enable users to better navigate
and understand changes in the kernel. These mechanisms include searching,
commit messages, files edited, modules edited, and two types of tree viewers.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/search.png}
	\caption{Search View}
	\label{fig:search}
\end{figure}

Searching allows a user to filter our commits and merges that are irrelevant.
The search mechanism breaks down the results by release version. A user can
further narrow down the search range using the commit date range. This commit
date refers to the date of the creation of the top-level merge. Commits and
merges that are returned may have a commit date beyond the given range if they
were merged to a top-level merge within the date range. A user may then provide
a search text, filtering on the author name, the commit id, or keyword from the
log. Any part of the author name may show up in the results, including
searching by email address. The commit ID must be specified from the first
character to the last character. For example, the commit
`c267548755a184ef97301071300c1739a564e135' is returned when the user searches
for a commit id of `c26' in the 3.10 Linux kernel.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/search_results.png}
	\caption{Search Results}
	\label{fig:results}
\end{figure}

In the search results , the user is presented with the one-line log message
preview, the author's name and email, the date the commit was authored, and the
date the commit was committed. \evantodo{a better definition for commit date}
The commit date and author date will usually be the same, however, if the
commit has been rebased, the commit date will be different than the authored
date, and will always be after the authored date. The first and third entries
in figure \ref{fig:results} have been rebased in the past. \evan{We are unable
to show the rebases.}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/message_view.png}
	\caption{Commit Message}
	\label{fig:message}
\end{figure}

The first view displays the full commit log. From this, a user is able to see
hat they would see had they searched for the commit using git log. This doesn't
provide additional information to the other tools, but helps to complete the
functionality of the tool. This information provides a user with the
information about the content of the commit and who has looked over the commit
to ensure that it is good quality. The message for merges may also contain the
information about the commits that are being merged into a given merge. The
information within these messages is highly variable, and is completely
dependent on the author's style. As the user moves toward the top-level merge,
the quality of these messages generally improve.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/file_view.png}
	\caption{Commit Files}
	\label{fig:files}
\end{figure}

The second tab is the files tab. This tab provides information on what files
have been edited, how many lines were added, and how many lines were removed in
a given commit. This functionality is similar to the other tools available. Our
tree-based design model allows us to extend this functionality to merges, which
the other tools are unable to show. When a file is edited multiple times from
different commits within a merge, we simply add the added and removed lines to
the values already stored. \evan{At this time, we don't have a mechanism to
process the diff information to determine which lines were changed, and in what
order.}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/tree_view.png}
	\caption{Commit Tree View}
	\label{fig:files}
\end{figure}

The third tab shows the tree view. The tree view is what makes this tool unique
to the other tools. It provides a full view of the entire merge tree. It
originally centres at the current commit or merge, but allows a user to inspect
the other commits and merges surrounding it. A user may then navigate to any of
the commits by simply double-clicking on it.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/tree_zoom.png}
	\caption{Tree zoomed out}
	\label{fig:files}
\end{figure}

Some of the merge trees are very large, containing thousands of commits and
merges. Clicking on subtrees will cause them to minimize, only showing parts of
the tree that are of interest to the user. Furthermore, the user can zoom the
tree by scrolling the mouse wheel to see more of the topology of the tree, or
to see the details of a given part of the tree.

The last tab contains another type of tree view. This tree is in the form of
nested lists, and is designed to more closely model the tree hierarchy view of
file browsers. This tree only contains the commits and merges that are within
the subtrees of the current merge. A commit will never have any items in this
tab, as it is a leaf node, so it cannot contain subtrees. To accompany the
tree, we include breadcrumbs at the top. The last item in the breadcrumb list
is the current commit, the next item is the parent of the current commit, and
the first item is the top-level merge into the kernel.
